>

### 2019-05-22 paper/spinifex-paper.tex
checking that the few changes made are uploaded

Imagine holding the manip var, the red axis in Figure \ref{fig:step2},
one end fixed to the origin and moving it like a lever. This is
effectively the process of the radial manual to rotate the manip
variable into and out of the 2D projection (Figure \ref{fig:step3}). As
the variable is controlled, the manipulation space rotates about the
origin, the projection onto the horizontal projection plane
correspondingly moves. This is what happens in a manual tour. Generating
a sequence of values for the horizontal and vertical, angles produces a
path for the rotation of the manipulation space. This defines the
(orthonormally-constrained) rotation on the basis coefficients.

For a radial tour fix the (horizontal) angle within the projection
plane, \(\theta\), and define a sequence for the (vertical) angle coming
out of the projection plane, \(\phi\), bringing the initial value of
\(|\textbf{B}_k|\) to a maximum and then to zero before returning to the
initial position. Alternatively, for an \emph{oblique} manual tour,
capture the user manipulation directly on the \(XY\) of the projection
plane.

>>>>

Imagine moving the axis of manip var, the red line in Figure
\ref{fig:step2}, like a lever. This is effectively the process of the
radial manual control, that rotates the manip variable into and out of
the 2D projection (Figure \ref{fig:step3}). As the variable is
controlled, the manipulation space rotates, and the projection onto the
horizontal projection plane correspondingly changes. This is a manual
tour. Generating a sequence of values for the horizontal and vertical
angles produces a path for the rotation of the manipulation space. This
defines the (orthonormally-constrained) rotation on the basis
coefficients.

For a radial tour, fix the (horizontal) angle within the projection
plane, \(\theta\), and define a sequence for the (vertical) angle,
\(\phi\), defining movement out of the plane, that changes the initial
value of \(|\textbf{B}_k|\) to a maximum of 1, and then to 0, before
returning to the initial value.

### 2019-05-22 paper/spinifex_paper.Rmd
checking that the few changes made are uploaded

<!-- illustration of axis manip -->
Imagine holding the manip var, the red axis in Figure \ref{fig:step2}, one end fixed to the origin and moving it like a lever. This is effectively the process of the radial manual to rotate the manip variable into and out of the 2D projection (Figure \ref{fig:step3}). As the variable is controlled, the manipulation space rotates about the origin, the projection onto the horizontal projection plane correspondingly moves. This is what happens in a manual tour. Generating a sequence of values for the horizontal and vertical, angles produces a path for the rotation of the manipulation space. This defines the (orthonormally-constrained) rotation on the basis coefficients.

<!-- describe manip var path -->
For a radial tour fix the (horizontal) angle within the projection plane, $\theta$, and define a sequence for the (vertical) angle coming out of the projection plane, $\phi$, bringing the initial value of $|\textbf{B}_k|$ to a maximum and then to zero before returning to the initial position. Alternatively, for an *oblique* manual tour, capture the user manipulation directly on the $XY$ of the projection plane.

>>>>

<!-- illustration of axis manip -->
Imagine moving the axis of manip var, the red line in Figure \ref{fig:step2}, like a lever. This is effectively the process of the radial manual control, that rotates the manip variable into and out of the 2D projection (Figure \ref{fig:step3}). As the variable is controlled, the manipulation space rotates, and the projection onto the horizontal projection plane correspondingly changes. This is a manual tour. Generating a sequence of values for the horizontal and vertical angles produces a path for the rotation of the manipulation space. This defines the (orthonormally-constrained) rotation on the basis coefficients.

<!-- describe manip var path -->
For a radial tour, fix the (horizontal) angle within the projection plane, $\theta$, and define a sequence for the (vertical) angle, $\phi$, defining movement out of the plane, that changes the initial value of $|\textbf{B}_k|$ to a maximum of 1, and then to 0, before returning to the initial value.
